---
title: "Volatility Modelling in Apple Stocks "
output: html_notebook
---

## *This paper is an attmept to understand the volatility in the stock prices for apple* : 

## First Things First , Lets get a data set for apple since 2006
```{r}

library(tseries)
library(zoo)
library(xts)
library(ggfortify)
appl_stock<-read.csv("C:/Users/ltyagi.MOSAICINT/Downloads/AAPL (6).csv")
appl_stock
appl_stock1<-appl_stock[c(1,5)]
appl_stock1
ap<-ts(appl_stock1$Close,start=c(2011,11,20),frequency = 365)

autoplot(ap,ts.colour='blue')+
  ggtitle("Stock Data for Apple since 2006 ")


```
# Lets observe the retruns on the stock , on daily basis : 


```{r}
library(ggplot2)
library(ggfortify)
library(tseries)
autoplot( (diff(ap)/ap[-length(ap)]),ts.colour = 'dodgerblue4')+
  ggtitle("log returns for apple")+ 
    ylab("log returns")+xlab("Year")
```


## There can be easily seen the period of volatility in Apple stocks in time intervals, 
so under these assumptions we need to fit a grach model on the same and analyse the volatility .
```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

